Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-15 disc_paper/disc20clustering.tex
Journal

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{decorations.pathreplacing} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{.55\textwidth}
		\hspace{15mm}
		\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
		\useasboundingbox  (-3mm,-5mm) rectangle (0mm,10mm);
		%cluster 1
		\def\x{30}
		\def\w{15}
		%Shape: Rectangle
		\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
		%Straight Lines
		\draw   (0,20) -- (15,20) ;
		% Text Node
		\draw (8,10) node (b1)  {$b_{1}$} ;
		% Text Node
		\draw (8,30) node (a4)   {$a_{4}$};

		%cluster 2
		\draw   (\x,0) -- (\w+\x,0) -- (\w+\x,40) -- (\x,40) -- cycle ;
		\draw   (\x,20) -- (\w+\x,20) ;
		% Text Node
		\draw (\x+8,10) node (b2)   {$b_{2}$};
		% Text Node
		\draw (\x+8,30) node (a1)   {$a_{1}$};

		\draw[thick,dotted, shorten <= -6pt, shorten >= -6pt] (a4)  -- (a1);
		\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a4) -- (b2);

		%cluster 3
		\draw   (2*\x,0) -- (\w+2*\x,0) -- (\w+2*\x,40) -- (2*\x,40) -- cycle ;
		\draw    (2*\x,20) -- (\w+2*\x,20) ;
		% Text Node
		\draw (2*\x+8,10) node (b3)   {$b_{3}$};
		% Text Node
		\draw (2*\x+8,30) node (a2)   {$a_{2}$};
		\draw[thick,dotted, shorten <= -4pt, shorten >= -3pt] (b2)  -- (b3);
		\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (b2) -- (a2);

		%cluster 4
		\draw   (3*\x,0) -- (\w+3*\x,0) -- (\w+3*\x,40) -- (3*\x,40) -- cycle ;
		\draw    (3*\x,20) -- (\w+3*\x,20) ;
		% Text Node
		\draw (3*\x+8,10) node (b4)   {$b_{4}$};
		% Text Node
		\draw (3*\x+8,30) node (a3)   {$a_{3}$};
		\draw[thick,dotted, shorten <= -4pt, shorten >= -3pt] (a2)  -- (a3);
		\draw [->,blue, shorten <= -5pt, shorten >= -2pt] (a2) -- (b4);

		\draw[thick, dotted,  shorten <= -3pt, shorten >= -5pt]  (b4) to[out=-100,in=-80] (b1);
		% arrow
		\draw[->, blue,shorten <= -3pt, shorten >= -4pt]  (b4) 
		to [out=-108,in=-130, distance=17mm]  (a4);
		\end{tikzpicture}
	\end{minipage}\hfill
	%
	\begin{minipage}[b]{.45\textwidth}
		\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
		\useasboundingbox  (0mm,-5mm) rectangle (0mm,10mm);
		%cluster 1
		\def\x{30}
		\def\w{15}
		%Shape: Rectangle
		\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
		%Straight Lines
		\draw   (0,20) -- (15,20) ;
		% Text Node
		\draw (8,10) node (b1)  {$b_{1}$} ;
		% Text Node
		\draw (8,30) node (b4)   {$b_{4}$};

		%cluster 2
		\draw   (\x,0) -- (\w+\x,0) -- (\w+\x,40) -- (\x,40) -- cycle ;
		\draw   (\x,20) -- (\w+\x,20) ;
		% Text Node
		\draw (\x+8,10) node (a4)   {$a_{4}$};
		% Text Node
		\draw (\x+8,30) node (a1)   {$a_{1}$};

		%cluster 3
		\draw   (2*\x,0) -- (\w+2*\x,0) -- (\w+2*\x,40) -- (2*\x,40) -- cycle ;
		\draw    (2*\x,20) -- (\w+2*\x,20) ;
		% Text Node
		\draw (2*\x+8,10) node (b3)   {$b_{3}$};
		% Text Node
		\draw (2*\x+8,30) node (b2)   {$b_{2}$};

		%cluster 4
		\draw   (3*\x,0) -- (\w+3*\x,0) -- (\w+3*\x,40) -- (3*\x,40) -- cycle ;
		\draw    (3*\x,20) -- (\w+3*\x,20) ;
		% Text Node
		\draw (3*\x+8,10) node (a2)   {$a_{2}$};
		% Text Node
		\draw (3*\x+8,30) node (a3)   {$a_{3}$};
		\end{tikzpicture}
	\end{minipage}
	\caption{
		Dashed lines represent requests.
		An arrow from node $x$ to node $y$ indicates that $x$  replaces $y$.
		\OPT collocates 4 pairs from the left partition, with  4 migrations,
		resulting in the right partition.
	}
	\label{fig:cyclic}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\begin{tikzpicture}
	\draw [->] (-10mm,0) -- (5,0);
	\draw [dotted] (-13mm,0) -- (-10mm,0);

	\draw [decorate,decoration={brace,amplitude=3pt}] (5mm,0.15) -- (45mm,0.15)
	node [black,midway,above=1pt,xshift=1pt] {$R_{t}$};

	\draw [decorate,decoration={brace,amplitude=3pt}, yshift=-18pt] (25mm,0.15) -- (-7mm,0.15)
	node [black,midway,below=1pt,xshift=1pt] {$R_{t'}$};

	\draw [] (45mm,2pt) -- (45mm,-2pt)
	node [black,midway,below=0pt,xshift=1pt] {$t$};

	% tick
	\draw [] (25mm,2pt) -- (25mm,-2pt)
	node [black,midway,below=0pt,xshift=1pt] {$t'$};
	% tick
	\draw [] (5mm,2pt) -- (5mm,-2pt)
	node [black,midway,below=0pt,xshift=1pt] {$t''$};
	% tick
	\draw [] (-7mm,2pt) -- (-7mm,-2pt)
	node [black,midway,below=0pt,xshift=1pt] {};

	\draw [line width=0.33mm, red] (5mm,0) -- (25mm,0) 
	node [black,midway,below=-2pt,xshift=1pt] {$\sigma_{\{u,w\}}$};

	\draw [] (25mm,0) -- (45mm,0) 
	node [black,midway,below=-2pt,xshift=1pt] {$\sigma_{\{u,v\}}$};

	\draw [] (5mm,2pt) -- (5mm,-2pt)
	node [black,midway,below=0pt,xshift=1pt] {$t''$};
	%% vertical arrow 
	%\draw [->] (3mm,14pt) -- (4.4mm,4pt)
	%node [black,midway,above=0pt,xshift=-4pt] {separation of  $\{u,w\}$};
	%% vertical arrow 
	%\draw [->] (30mm,-24pt) -- (26.5mm,-7pt)
	%node [black,midway,below=0pt,xshift=5pt, yshift=-5pt] {separation of  $\{u,v\}$};
	\end{tikzpicture}
	\caption{
		Illustration of the timeline used in the proof of Theorem \ref{thm:k=2}.
		Requests in $R_t$  are only to  $\{u,w\}$ and $\{u,v\}$,
		which  arrive  during the interval $(t'',t]$.
		Similarly,
		request in $R_{t'}$  are to $\{u,w\}$ and some other pair, irrelevant to the analysis.
		Hence, requests to $\{u,w\}$ are included in at most two such sets,
		which are $R_{t'}$ and $R_t$.
		This is because their intervals overlap on $(t'',t']$, shown with red thick line.
	}
	\label{fig:timeline}
\end{figure}

@@

%\section{Additional Figures}
%\begin{comment}
%\end{comment}

>>>>

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{decorations.pathreplacing} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}
 \usepackage{standalone}

@@

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{.5\textwidth}	
				\centering	
		\includestandalone{figs/k=2_a}
	\end{minipage}%
	%
	\begin{minipage}[b]{.5\textwidth}
		\centering
				\includestandalone{figs/k=2_b}
	\end{minipage}
	\caption{
		Dashed lines represent requests.
		An arrow from node $x$ to node $y$ indicates that $x$  replaces $y$.
		\OPT collocates 4 pairs from the left partition, with  4 migrations,
		resulting in the right partition.
	}
	\label{fig:cyclic}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includestandalone{figs/timeline}
	\caption{
		Illustration of the timeline used in the proof of Theorem \ref{thm:k=2}.
		Requests in $R_t$  are only to  $\{u,w\}$ and $\{u,v\}$,
		which  arrive  during the interval $(t'',t]$.
		Similarly,
		request in $R_{t'}$  are to $\{u,w\}$ and some other pair, irrelevant to the analysis.
		Hence, requests to $\{u,w\}$ are included in at most two such sets,
		which are $R_{t'}$ and $R_t$.
		This is because their intervals overlap on $(t'',t']$, shown with red thick line.
	}
	\label{fig:timeline}
\end{figure}

@@
